What is MaxEnt?

### 2014-11-24 ms.tex
Random writing

@@

\begin{eqnarray}
\begin{array}{|c|c|c|}
\hline
	&	S	& \bar{S}\\
\hline
H_1 & 0.25  & 0.25\\
H_2 & 0.05 & 0.45\\
\hline
\end{array}
\end{eqnarray}

@@

\section{MaxEnt and Bayesian Inference}

\section{MaxEnt and Hierarchical Bayesian Models}

\begin{thebibliography}{}
\end{thebibliography}

>>>>

\section{A Special Case: Expected Values}\label{sec:expectations}
Refer to Jaynes here...I don't want to present all the details.

@@

\begin{eqnarray}
\begin{array}{|c|c|c|}
\hline
	&	S	& \bar{S}\\
\hline
H_1 & 0.25  & 0.25\\
\hline
H_2 & 0.05 & 0.45\\
\hline
\end{array}
\end{eqnarray}

@@

\section{MaxEnt and Bayesian Inference}\label{sec:bayes}

\section{MaxEnt and Hierarchical Bayesian Models}
Suppose we have a prior distribution $q(\mathbf{x})$ describing a state of
knowledge about a vector of quantities $\mathbf{x}$. Consider some
function of the unknowns, such as $f(\mathbf{x}) = \sum_{i=1}^N x_i$.
If the value of $f$ is known, then our distribution for $\mathbf{x}$ can
be updated as in Section~\ref{sec:bayes}. If we receive testable information
about the expected value of $f$, then our distribution for $\mathbf{x}$ can
be updated as in Section~\ref{sec:expectations}.

In this section we'll look at a different kind of testable information that
relates to $f$, but is not the expected value. What if we receive testable
information about the marginal distribution for $f$?

To keep things concrete, suppose all of the unknown parameters are positive,
and our prior is an improper uniform distribution:

\begin{eqnarray}
q(\mathbf{x}) \propto
\left\{
\begin{array}{lr}
1, & \forall x_i > 0\\
0, & \textnormal{otherwise}.
\end{array}
\right.
\end{eqnarray}

\begin{thebibliography}{}
Jaynes, E. T., 1979, `Where do we Stand on Maximum Entropy?' in The Maximum Entropy Formalism, R. D. Levine and M. Tribus (eds.), M. I. T. Press, Cambridge, MA, p. 15
\end{thebibliography}
